Clouds and Sensitivities Across a Hierarchy of GFDL CMIP6 Models

### 2020-04-24 Silvers_cfmip_SinglePanelFig.tex
addition of three tex files that are used to generate multipanel figures

\begin{figure}
  \centering
  \begin{subfigure}{0.48\textwidth}
  \includegraphics[width=\linewidth]{cfmipfigs/CRE_net_ceres_cfmipExps.eps}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
  \includegraphics[width=\linewidth]{cfmipfigs/CRE_SWonly_feedback_amip.eps}
\end{subfigure}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}{0.48\textwidth}
    \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cf_warming.eps}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
  \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cf_warming_amipbias.eps}
\end{subfigure}
\end{figure}
